checkData

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd

@@

@@

```{r}
# update exclusion_reason_final column when primary and secondary coder disagree on reason to exclude.
d_articles <- d_articles %>%
  mutate(exclusion_reason_final = case_when(
    sampleID == 'random' & article_id == '14' ~ exclusion_reason_primary,
    sampleID == 'random' & article_id == '35' ~ exclusion_reason_primary,
    sampleID == 'random' & article_id == '54' ~ exclusion_reason_secondary,
    sampleID == 'random' & article_id == '73' ~ exclusion_reason_primary,
    sampleID == 'random' & article_id == '78' ~ exclusion_reason_primary,
    sampleID == 'prominent' & article_id == '29' ~ "RETRACTED", # the article was withdrawn, retracted seems like the closest fit among out labels
    sampleID == 'prominent' & article_id == '37' ~ exclusion_reason_primary,
    sampleID == 'prominent' & article_id == '39' ~ exclusion_reason_primary,
    sampleID == 'prominent' & article_id == '46' ~ exclusion_reason_primary,
    sampleID == 'prominent' & article_id == '54' ~ exclusion_reason_secondary,
    TRUE ~ exclusion_reason_final # if none of the above, retain whatever is in this column already
  ))
```
Finally, let's check anything that was excluded with the reason "OTHER".

```{r}
d_articles %>% filter(exclusion_reason_final == "OTHER") %>% select(article_id, sampleID)
```
Article ID 68 can reclassifed as "NO ACCESS" and for the other three articles we can create a new post-hoc exclusion category "CONFERENCE ABSTRACT".

```{r}
d_articles <- d_articles %>%
  mutate(exclusion_reason_final = case_when(
    sampleID == 'random' & article_id == '68' ~ "NO ACCESS",
    sampleID == 'prominent' & article_id == '2' ~ "CONFERENCE ABSTRACT",
    sampleID == 'prominent' & article_id == '56' ~ "CONFERENCE ABSTRACT",
    sampleID == 'prominent' & article_id == '85' ~ "CONFERENCE ABSTRACT",
    TRUE ~ exclusion_reason_final # if none of the above, retain whatever is in this column already
  ))
```
We should now have resolved coding for all exclusion decisions and exclusion reasons in d_articles

```{r}
d_articles <- d_articles %>%
  mutate(ppc_linked_final = case_when(
    exclusion_final == "EXCLUDE" ~ NA_character_, # if article is excluded, use NA
    sampleID == 'prominent' & article_id == '38' ~ ppc_linked_secondary,
    exclusion_final == "RETAIN" & exclusion_primary == "RETAIN" ~ ppc_linked_primary,
    exclusion_final == "RETAIN" & exclusion_secondary == "RETAIN" ~ ppc_linked_secondary,
    TRUE ~ "ERROR" # if none of the above, retain whatever is in this column already
  ))
```
# Resolve coding disagreements in journals data

```{r}
d_journals_final <- d_journals %>%
  filter(coder_id == "FINAL (TEH)") %>% # select only the final coding
  select(-coder_id, -timestamps) # drop the coder_id and timestamps columns
```
# Journals data - exclusions

>>>>

```{r}
# update exclusion_reason_final column when primary and secondary coder disagree on reason to exclude.
d_articles <- d_articles %>%
  mutate(exclusion_reason_final = case_when(
    sampleID == 'random' & article_id == '14' ~ exclusion_reason_primary,
    sampleID == 'random' & article_id == '35' ~ exclusion_reason_primary,
    sampleID == 'random' & article_id == '54' ~ exclusion_reason_secondary,
    sampleID == 'random' & article_id == '73' ~ exclusion_reason_primary,
    sampleID == 'random' & article_id == '78' ~ exclusion_reason_primary,
    sampleID == 'prominent' & article_id == '29' ~ "RETRACTED", # the article was withdrawn, retracted seems like the closest fit among out labels
    sampleID == 'prominent' & article_id == '37' ~ exclusion_reason_primary,
    sampleID == 'prominent' & article_id == '39' ~ exclusion_reason_primary,
    sampleID == 'prominent' & article_id == '46' ~ exclusion_reason_primary,
    sampleID == 'prominent' & article_id == '54' ~ exclusion_reason_secondary,
    TRUE ~ exclusion_reason_final # if none of the above, retain whatever is in this column already
  ))
```

Finally, let's check anything that was excluded with the reason "OTHER".

```{r}
d_articles %>% filter(exclusion_reason_final == "OTHER") %>% select(article_id, sampleID)
```

Article ID 68 can reclassifed as "NO ACCESS" and for the other three articles we can create a new post-hoc exclusion category "CONFERENCE ABSTRACT".

```{r}
d_articles <- d_articles %>%
  mutate(exclusion_reason_final = case_when(
    sampleID == 'random' & article_id == '68' ~ "NO ACCESS",
    sampleID == 'prominent' & article_id == '2' ~ "CONFERENCE ABSTRACT",
    sampleID == 'prominent' & article_id == '56' ~ "CONFERENCE ABSTRACT",
    sampleID == 'prominent' & article_id == '85' ~ "CONFERENCE ABSTRACT",
    TRUE ~ exclusion_reason_final # if none of the above, retain whatever is in this column already
  ))
```

We should now have resolved coding for all exclusion decisions and exclusion reasons in d_articles

```{r}
d_articles <- d_articles %>%
  mutate(ppc_linked_final = case_when(
    exclusion_final == "EXCLUDE" ~ NA_character_, # if article is excluded, use NA
    sampleID == 'prominent' & article_id == '38' ~ ppc_linked_secondary,
    exclusion_final == "RETAIN" & exclusion_primary == "RETAIN" ~ ppc_linked_primary,
    exclusion_final == "RETAIN" & exclusion_secondary == "RETAIN" ~ ppc_linked_secondary,
    TRUE ~ "ERROR" # if none of the above, retain whatever is in this column already
  ))
```

# Resolve coding disagreements in journals data

```{r}
d_journals_final <- d_journals %>%
  filter(coder_id == "FINAL (TEH)") %>% # select only the final coding
  select(-coder_id, -timestamps) # drop the coder_id and timestamps columns
```

# Journals data - exclusions

## Harmonize peer review polic

For PPC peer review policy we need to harmonize differences in data entry formatting.

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>% 
  mutate(review_harmonized = str_remove_all(review, pattern = '"'), #  remove any quotation marks
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (provide number of references below), ")),# remove data entry question text
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
         ref_harmonized = case_when(
           ref_harmonized == "20 not hard-and-fast limits" ~ "20",
           ref_harmonized == "265 lines of text including references" ~ "NOT STATED",
           ref_harmonized == "contributions may have up to 15 references" ~ "15",
           ref_harmonized == "Included in 16 page overall limit" ~ "NOT STATED",
           ref_harmonized == "No more than 5 references" ~ "5",
           ref_harmonized == "overall limit is 265 lines of text including references" ~ "NOT STATED",
           TRUE ~ ref_harmonized
         )) 
```

# Journals data — add JIF and COPE

@@

For the random journals we can find the JIFs in the prominent journal sample. Some journals do not have a JIF because they haven't been indexed long enough. We manually checked all of these journals. One JIF needed to be added manually for the journal "Journal of Psychology and Theology". The 2021 JIF for this journal is .80.

@@
